Practical Considerations for Lomb-Scargle Periodic Analysis

### 2016-12-11 paper.tex
Finish convolution diagram

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig04_Convolution_Diagram}
  \caption{Visualization of a convolution as often used for kernel smoothing.
    The normalized tophat-shaped window function slides across the domain (upper panel),
    such that at each point the mean of the values within the window are
    used to compute the smoothed function (lower panel).
    \figlabel{convolution}}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig05_Convolution_Theorem}
  \caption{Visualization of a convolution used for kernel smoothing
    \figlabel{convolution_theorem}}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig04_Convolution_Diagram}
  \caption{Visualization of a convolution between a continuous signal and a tophat smoothing kernel.
    The normalized tophat-shaped window function slides across the domain (upper panel),
    such that at each point the mean of the values within the window are
    used to compute the smoothed function (lower panel).
    \figlabel{convolution}}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig05_Convolution_Theorem}
  \caption{Visualization of the Convolution theorem as used to compute the
    result in \fig{convolution}. The key is that the Fourier transform of
    a convolution is the pointwise product of the two Fourier transforms.
    \figlabel{convolution_theorem}}
\end{figure}
